---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body 
{
  font-family: "Times New Roman", Times, serif;
}

```

## Investigating New Zealand Warriors Merchandise Trends 

The nature of this investigation was to determine how common it is to see people supporting the local Rugby League team, the New Zealand Warriors. Along with this, I was also interested in finding where people wear this merchandise. 

```{r}
# loading in the tidyverse package
library(tidyverse)

# reading in the csv file and naming it data
data <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQX8kEjRVJnIopxlIckozy2C-mRnZIkZ-fCTq5chuGDYkb2zfstvvcr6cPkq0lrdxD61ewDaU1BfKSa/pub?gid=628837099&single=true&output=csv"

# naming the csv file logged data and renaming all the variables
logged_data <- read_csv(data) %>%
  rename(number_people = 2,
       merchandise_type = 3,
       location = 4)
# finding the maximum number of people that were seen wearing the merchandise at once
max(logged_data$number_people)

# finding the most commonly worn piece of NZ Warriors merchandise
most_common <- max(logged_data$merchandise_type)

# finding the least common place to wear NZ Warriors merchandise
min(logged_data$location)

# least common item of NZ Warriors merchandise
least_common_item <- min(logged_data$merchandise_type)

```

It was found that the most common place to find people wearing New Zealand Warriors merchandise was 'r most_common'. 
It was also found that the least popular item of merchandise was 'r least_common_item'


```{r}
# bar plot of the various merchandise types
logged_data  %>%
  ggplot() +
  geom_bar(aes(x = merchandise_type,
           fill = merchandise_type))

# bar plot of the various locations
logged_data  %>%
  ggplot() +
  geom_bar(aes(y = location,
               fill = location))

```








